Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-02-01 paperMSR.tex
add limited knowleadge image

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause. We were unable to decide in 42 cases or due to our limited knowleadge about the code. The figure~\ref{fig:added} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines. In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.\gema{Me faltaria el ejemplo de limited knowledge, cuando encuentre uno bueno lo anado}
We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.

@@

%\begin{figure}[ht]
%\centering
%\includegraphics[height=2cm]{unknown.png}
%\label{fig:9}       % Give a unique label
%\caption{Example of unknowleadge where we are unable to decide which previous commit caused the bug }
%\end{figure}
\begin{table}[htb]
\begin{center}
\begin{tabular}{lrr}
\toprule[0.3mm]
  & \multicolumn{1}{c}{Before} & \multicolumn{1}{c}{After} \\
  & \multicolumn{1}{c}{Deleting Noise} & \multicolumn{1}{c}{Deleting Noise} \\\hline
{Cause} & (152) 44\% & (152) 49\% \\[0ex]
{Not Cause} & (154) 44\% & (114) 37\% \\[0ex]
{Undecided} & (42) 12\% & (42) 14\% \\[0ex]
\bottomrule[0.3mm]
\end{tabular}
\caption{Number of times (and percentage) where the previous commit is the cause, not the cause or could not be classified, before and after deleting noise.}
\label{tab:responsability}
\end{center}
\end{table}

>>>>

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause. We were unable to decide in 42 cases or due to our limited knowleadge about the code. The figure~\ref{fig:added} shows the change done in the fix bug commit, on the left the lines before the fix commit and on the right the file after the fix commit with only additions lines. In this case, we cannot be able to know which previous commit could be the one that forgot added this lines, this is the reason why we classifyed as \textit{Undecied}.The figure ~\ref{fig:unknow} shows an example of limited knowleadge about which line could inserted the bug.
We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.

@@

\begin{figure}[ht]
\centering
\includegraphics[height=3.5cm]{unknowleadge.png}
\label{fig:unknow}       % Give a unique label
\caption{Example of unknowleadge where we are unable to decide which line contains the bug }
\end{figure}
\begin{table}[htb]
\begin{center}
\begin{tabular}{lrr}
\toprule[0.3mm]
  & \multicolumn{1}{c}{Before} & \multicolumn{1}{c}{After} \\
  & \multicolumn{1}{c}{Deleting Noise} & \multicolumn{1}{c}{Deleting Noise} \\\hline
{Cause} & (152) 44\% & (152) 49\% \\[0ex]
{Not Cause} & (154) 44\% & (114) 37\% \\[0ex]
{Undecided} & (42) 12\% & (42) 14\% \\[0ex]
\bottomrule[0.3mm]
\end{tabular}
\caption{Number of times (and percentage) where the previous commit is the cause, not the cause or could not be classified, before and after deleting noise.}
\label{tab:responsability}
\end{center}
\end{table}
